Immutable Source-Mapped Abstract Syntax Tree:\ \, \\ A Design Pattern for Refactoring Engine APIs

### 2017-09-27 paper.tex
Reworded basic forces section
Basic forces grammar
Removed figure periods

There are several basic forces at work in this problem:

@@

Traditionally, program syntax is made available through abstract syntax trees.

@@

\begin{wrapfigure}{r}{3in} % r is right, R is float right
% Original image is 4.624 x 10.651 in
\includegraphics[scale=0.62]{jdt-ast.eps}
%\caption{Visualization of the Eclipse Java Development Tools' abstract syntax
%tree for the following program: \\
%\ \\
%\centerline{\parbox{2in}{\ttt{\noindent public class Example \{ \\
%\hspace*{.2em} public int FIVE = 5; \\
%\}
%}}} \\
%\ \\
%The highlighted node---a \textit{VariableDeclarationFragment}---corresponds to
%the eight-character substring \ttt{FIVE = 5}, which begins with the 36th
%character in the source code.
%}
\caption{Visualization of an AST produced by the Eclipse Java Development Tools
(JDT).\vspace*{-4em}}
\label{fig:jdt-ast}
\end{wrapfigure}

@@

\subsection{Mutable vs.\ Immutable ASTs}
\label{ss:manip}

@@

\begin{figure}[!bt]
\begin{center}
\includegraphics[width=.9\textwidth]{seq-diagram.eps}
\end{center}
\caption{Sequence diagram illustrating use of a Rewriter to modify source code.}
\label{fig:seq-diagram}
\end{figure}

@@

\begin{figure}
\begin{center}
\includegraphics[scale=0.30]{swapStatements.eps}
\caption{The \emph{swapStatements} method.\vspace*{-4em}}
\label{fig:swapStatements}
\end{center}
\end{figure}

>>>>

There are several basic requirements that a solution API must meet.

@@

Traditionally, fine-grained program syntax is made available through 
abstract syntax trees.

@@

\begin{wrapfigure}{r}{3in} % r is right, R is float right
% Original image is 4.624 x 10.651 in
\includegraphics[scale=0.62]{jdt-ast.eps}
%\caption{Visualization of the Eclipse Java Development Tools' abstract syntax
%tree for the following program: \\
%\ \\
%\centerline{\parbox{2in}{\ttt{\noindent public class Example \{ \\
%\hspace*{.2em} public int FIVE = 5; \\
%\}
%}}} \\
%\ \\
%The highlighted node---a \textit{VariableDeclarationFragment}---corresponds to
%the eight-character substring \ttt{FIVE = 5}, which begins with the 36th
%character in the source code.
%}
\caption{Visualization of an AST produced by the Eclipse Java Development Tools
(JDT)\vspace*{-4em}}
\label{fig:jdt-ast}
\end{wrapfigure}

@@

\subsection{Mutability and ASTs}
\label{ss:manip}

@@

\begin{figure}[!bt]
\begin{center}
\includegraphics[width=.9\textwidth]{seq-diagram.eps}
\end{center}
\caption{Sequence diagram illustrating use of a Rewriter to modify source code}
\label{fig:seq-diagram}
\end{figure}

@@

\begin{figure}
\begin{center}
\includegraphics[scale=0.30]{swapStatements.eps}
\caption{The \emph{swapStatements} method\vspace*{-4em}}
\label{fig:swapStatements}
\end{center}
\end{figure}
